A Way Forward in Parallelising Dynamic Languages

### 2014-05-05 talk/icooolps2014/position-paper.tex
Move the table to page 3.
add concluding sentence

Following the above argumentation for each approach we assembled a
general overview in Table \ref{tab:comparison}. The general picture is
everything else than clear. It looks like HTM may be a good solution
to replace the GIL in the near future. Current implementations are
however far too limiting and do not provide good scaling.

@@

One way to get more performance is to develop STM systems that make
better use of low-level features in existing OS kernels.  We are
currently working on a STM system that makes use of several such
features like virtual memory and memory segmentation.  We further
tailor the system to the discussed use case which gives us an
advantage over other STM systems that are more general. With this
approach, initial results suggest that we can keep the overhead of STM
well below 50\%. A hybrid TM system, which also uses HTM to accelerate
certain tasks, looks like a very promising direction of research
too. We believe that further work to reduce the overhead of STM is
very worthwhile.

@@

>>>>

Following the above argumentation for each approach, we assembled a
general overview in Table \ref{tab:comparison}. The general picture is
everything else than clear. It looks like HTM may be a good solution
to replace the GIL in the near future. Current implementations are
however far too limiting and do not provide good scaling.

@@

One way to get more performance is to develop STM systems that make
better use of low-level features in existing OS kernels.  We are
currently working on a STM system that makes use of several such
features like virtual memory and memory segmentation.  We further
tailor the system to the discussed use case which gives us an
advantage over other STM systems that are more general. With this
approach, initial results suggest that we can keep the overhead of STM
well below 50\%. A hybrid TM system, which also uses HTM to accelerate
certain tasks, looks like a very promising direction of research
too.

We believe that further work to reduce the overhead of STM is
very worthwhile. In fact, considering some analogies that have been
drawn between garbage collection and transactional memory \cite{dan07},
we believe that it is worthwhile to focus the STM research more
specifically on the context shown in this paper --- for use in
implementations of high-level languages, rather than as a tool
directly used by the programmer.

@@

\bibitem{dan07}
  Dan Grossman. 2007. The transactional memory / garbage collection
  analogy. \emph{In Proceedings of the 22nd annual ACM SIGPLAN
    conference on Object-oriented programming systems and
    applications} (OOPSLA '07).
